\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[default]{roboto}
\input{glyphtounicode}

% Roboto is a modern sans-serif font designed by Google, perfect for tech industry resumes

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Dimitri E. Lavin} \\ \vspace{1pt}
    \small Charlotte, NC | \href{mailto:dimitrilavin@gmail.com}{dimitrilavin@gmail.com} | 704.441.1704 | \href{http://www.dimitrilavin.com}{dimitrilavin.com} | \href{https://github.com/dimitrilavin88}{github.com/dimitrilavin88}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, HTML/CSS, Java, Swift, MATLAB, C, Objective-C, C++, SQL} \\
     \textbf{Frameworks}{: React, Next.js, React Native, Node.js, Flask, FastAPI, Vite, Spring Boot} \\
     \textbf{ML/AI}{: scikit-learn, XGBoost, pandas, NumPy, TensorFlow, PyTorch, LightGBM, CatBoost} \\
     \textbf{Databases}{: PostgreSQL, MySQL, SQLite, MongoDB, Supabase} \\
     \textbf{Tools}{: Git/GitHub, VS Code, IntelliJ IDEA, AWS, Railway, Vercel, Render} \\
     \textbf{APIs}{: Google Calendar, Kaggle, RESTful} \\
     \textbf{Methodologies}{: Agile, Scrum, SDLC} \\
    }}
 \end{itemize}

 %-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Planno - Scheduling Platform}}{2024 - Present}
      \resumeItemListStart
        \resumeItem{Architected full-stack scheduling platform (Next.js, TypeScript, React) addressing meeting coordination conflicts. Solved via shareable booking links with real-time availability, enabling self-service scheduling eliminating back-and-forth communication. Integrated Google Calendar API for auto-sync and Apple Calendar downloads.}
        \resumeItem{Engineered Supabase/PostgreSQL backend with Row Level Security policies; deployed on Vercel with edge functions enabling calendar event creation and dashboard sharing.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{TastyFood - Food Ordering Platform}}{2024 - Present}
      \resumeItemListStart
        \resumeItem{Designed full-stack ordering platform (React, Java Spring Boot) solving 15-30\% revenue loss to third-party services. Eliminated commission fees through direct customer ordering via role-based dashboards, giving restaurants control over customer relationships.}
        \resumeItem{Implemented Spring Boot REST APIs, JWT authentication and PostgreSQL. Built React components for order management, payment processing, and delivery workflows; deployed on Railway for scalable microservices.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Premier League MVP Predictor}}{2024 -- Present}
      \resumeItemListStart
        \resumeItem{Engineered XGBoost regression model replacing subjective MVP selection with data-driven analysis. Trained on player statistics (goals, assists, clean sheets, influence) to predict performance and identify top 25 MVP candidates.}
        \resumeItem{Built FastAPI application with Kaggle API dataset ingestion and preprocessing. Implemented RESTful endpoints for predictions; deployed on Render with CORS middleware enabling concurrent requests.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Personal Portfolio Website}}{2021 -- Present}
      \resumeItemListStart
        \resumeItem{Developed responsive portfolio website showcasing projects with interactive cards, problem-solution narratives, and tech stacks. Implemented dark mode, smooth scrolling, and responsive design using HTML, CSS, and JavaScript.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Southern Methodist University, Lyle School of Engineering}{Aug 2023 - Dec 2025}
      {MS in Computer Science, AI Specialization; GPA: 3.5}{}
    \resumeSubheading
      {University of North Carolina at Chapel Hill}{Aug 2018 - May 2022}
      {BS in Computer Science, BA in Mathematics; GPA: 3.389}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SPED Paraprofessional}{Sept 2023 - Present}
      {Jefferson School District 251}{}
      \resumeItemListStart
        \resumeItem{Facilitate SPED instruction by developing behavioral and academic goals, implementing progress tracking, and guiding achievement.}
      \resumeItemListEnd

    \resumeSubheading
      {Ward Executive Secretary}{Oct 2024 - Present}
      {The Church of Jesus Christ of Latter-Day Saints}{}
      \resumeItemListStart
        \resumeItem{Coordinate leadership operations by organizing meetings, preparing agendas, managing scheduling, and facilitating communication.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Science Tutor}{Aug 2018 - May 2022}
      {UNC Learning Center and Personal Tutoring}{}
      \resumeItemListStart
        \resumeItem{Delivered instruction in programming (Python, Java, MATLAB) and advanced mathematics, emphasizing data structures, algorithms, and OOP.}
      \resumeItemListEnd

    \resumeSubheading
      {Teachers' Assistant - APPL 101: Exploring Engineering}{Aug 2021 - Dec 2021}
      {University of North Carolina at Chapel Hill}{}
      \resumeItemListStart
        \resumeItem{Instructed MATLAB modeling and provided support for engineering assignments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}

